ESRC SDAI Application - Understanding domestic abuse using Big Data

### 2019-07-18 JeS_fields.tex
Anna update

1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales as well as its consequences. Rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, providing a deeper understanding of the environments perpetuating domestic abuse. While we will only use UK data, these findings will likely to be relevant for researchers outside the UK.

2) To translate our research into impact by delivering applicable insights for the relevant agencies, including the police and policy-makers. Our results will provide the police with important information to help the optimal geographical and temporal allocation of resources and improving recording practices. These insights will also help the government to design more effective intervention campaigns.

3) To utilise the rich information contained in the CSEW to explore the predictors and consequences of domestic abuse victimisation. In spite of the detailed information contained in the CSEW about respondents, we are not aware of any non-exploratory study using the CSEW to explore the predictors and consequences of domestic abuse victimisation in England and Wales.

@@

health outcomes - consequences

@@

economists - establishing the causal effect of domestic abuse victimisation/witnessing domestic abuse on well-being and other socio-economic outcomes

@@

>>>>

1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales. Rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, providing a deeper understanding of the environments perpetuating domestic abuse. While we will only use UK data, these findings will likely to be relevant for researchers outside the UK.

2) To improve our understanding of the costs of domestic abuse, by investigating the causal effect of victimisation on a variety of socio-economic outcomes. Current cost estimates by the government do not take into account how educational attainment, income and employment status of victims are affected by victimisation and witnessing abuse as a child \cite{costs}.

3) To translate our research into impact by delivering applicable insights for the relevant agencies, including the police and policy-makers. Our results will provide the police with important information to help the optimal geographical and temporal allocation of resources and improving recording practices. These insights will also help the government to design more effective intervention campaigns.

4) To utilise the rich information contained in the CSEW to explore the predictors and consequences of domestic abuse victimisation. In spite of the detailed information contained in the CSEW about respondents, we are not aware of any non-exploratory study using the CSEW to explore the predictors and consequences of domestic abuse victimisation in England and Wales.

@@

@@

economists - establishing the causal effect of domestic abuse victimisation/witnessing domestic abuse on well-being and other socio-economic outcomes
health outcomes - consequences

@@

1) characteristics of victims and understanding predictors of serious harm - police can use insights to prevent serious harm, characteristics of victims - expand on previous qualitative research (academics) and help policy-makers better target campaigns

2) reporting behaviour and police mis-recording - police can improve recording practices, understanding reporting behaviour can benefit behavioural scientists who work for the government

3) consequences - helps the government and academics by advancing our knowledge on the consequences of domestic abuse victimisation by improving the methodology of
